## Unsupervised Learning - K-means
#### By Alysha Velasquez
<br>

This project uses the USArrests dataset, which includes contains the number of arrests for murder, assault, and rape for each of the 50 states in 1973. It also contains the percentage of people in the state who live in an urban area.

Installing and loading required packages:
```{r}
library("cluster") ##for computing clustering
library("factoextra") ##for ggplot2-based data visualization

```

Data prep:
```{r}
# Load data
data("USArrests")
my_data <- USArrests

# Remove any missing value 
my_data <- na.omit(my_data)

# Scale variables
my_data <- scale(my_data)

# View the firt 5 rows
head(my_data, n = 5)

```


Clarifying distance measures:
```{r}
#Computing a distance matrix between the rows of a data matrix
res.dist <- get_dist(USArrests, stand = TRUE, method = "pearson")


#Visualizing a distance matrix
fviz_dist(res.dist, 
   gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))

```

Partitioning clustering:
```{r}
library("factoextra")
fviz_nbclust(my_data, kmeans, method = "gap_stat")

#compute and visualize k-means clustering
km.res <- kmeans(my_data, 3, nstart = 25)

# Visualize
library("factoextra")
fviz_cluster(km.res, data = my_data, frame.type = "convex")+
  theme_minimal()

```


